Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-06-20 supp_mat_complexity_selection.Rmd

  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))

  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  return(data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals[1, ],
                    upper = get_intervals[2, ],
                    t(get_bootstraps$t)))
}
```

@@

```{r Gall Size Fitness Landscape}

@@

## Control ----
RF_control_clutch_size <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = sort(distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
     sc.female_preference = 0),
  bootstraps=100)

## Treatment ----
RF_treatment_clutch_size <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = sort(distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
     sc.female_preference = 0),
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
  group_by(ID, Food_Web) %>%
  mutate(relative_fitness = fitness/mean(fitness)) %>%
  ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

@@

# unclear to me why the complex intervals are weird...
bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
  group_by(Food_Web) %>%
  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.clutch_size, y=relative_fitness)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```

@@

## Control ----
RF_control_female_preference <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0, 
     sc.female_preference = sort(distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
  bootstraps=100)

## Treatment ----
RF_treatment_female_preference <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = sort(distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
  group_by(ID, Food_Web) %>%
  mutate(relative_fitness = fitness/mean(fitness)) %>%
  ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

@@

# unclear to me why the complex intervals are weird...
bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
  group_by(Food_Web) %>%
  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.female_preference, y=relative_fitness)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```

>>>>

  # Absolute fitness
  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))

  get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  absolute_fitness_df <- data.frame(newdata, 
                    average = get_absolute_fitness(logistic_model), 
                    lower = get_intervals_absolute_fitness[1, ],
                    upper = get_intervals_absolute_fitness[2, ],
                    t(get_bootstraps_absolute_fitness$t))

  # Relative fitness
  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))

  get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])

  relative_fitness_df <- data.frame(newdata, 
                    average = get_relative_fitness(logistic_model), 
                    lower = get_intervals_relative_fitness[1, ],
                    upper = get_intervals_relative_fitness[2, ],
                    t(get_bootstraps_relative_fitness$t))
  # Organize data
  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
}
```

@@

Okay, I solved the interval problem with relative fitness. Now I want to see if I can smooth up the 95% interval plots, by just plotting these 95% bootstrapped reps, shouldn't they be smooth lines? Is it something weird with geom_ribbon?

```{r REVISED Gall Size Fitness Landscape}

## Control ----
RF_control_gall_size <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000), 
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=100)

## Treatment ----
RF_treatment_gall_size <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=1000),
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
  #group_by(ID, Food_Web) %>%
  #mutate(relative_fitness = fitness/mean(fitness)) %>%
  #ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
  #group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.gall_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```

```{r OLD Gall Size Fitness Landscape, eval=FALSE}

@@

## Control ----
RF_control_clutch_size <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(-1,1,length.out=1000),
     sc.female_preference = 0),
  bootstraps=100)

## Treatment ----
RF_treatment_clutch_size <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = seq(-1,1,length.out=1000),
     sc.female_preference = 0),
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, relative_fitness, -sc.clutch_size, -Food_Web) %>%
  #group_by(ID, Food_Web) %>%
  #mutate(relative_fitness = fitness/mean(fitness)) %>%
  #ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

@@

bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
  group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.clutch_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```

@@

## Control ----
RF_control_female_preference <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0, 
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=100)

## Treatment ----
RF_treatment_female_preference <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = 0,
     sc.clutch_size = 0,
     sc.female_preference = seq(-1,1,length.out=1000)), 
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, relative_fitness, -sc.female_preference, -Food_Web) %>%
  #group_by(ID, Food_Web) %>%
  #mutate(relative_fitness = fitness/mean(fitness)) %>%
  #ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

@@

# unclear to me why the complex intervals are weird...
bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
  #group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.female_preference, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```
